---
title: "owner_EthanWanlass.Rmd"
author: "Ethan Wanlass"
date: "9/5/2019"
output: html_document
---

## Part 1

Name? 
Ethan Wanlass

What do you tell people about your field of study at a party? 
I'm a math major, I don't really tell people about my field of study; people tend not to like talking about it.  

What are the three most important tools/strategies you use for organizing your work? 
  - Keep clear concise paths, folders and filenames. 
  - Space out your work. Easier to read makes work go faster. 
  - Give outlines beforehand so you can figure out the main points you want to address. 

Interesting fact about yourself? 
I'm deaf in my left ear. 

## Understanding Concepts 

You may work on this with your partner or individually. 

  1. Explain the difference between Git and Github.
     Git is on your local machine and is the tool that records your source code. Github records your work on a server, so both you and others can access it from anywhere (as long as it's        public)
  
  2. Can Git and Github be used independently? Why don't we do so? Describe the advantages and disadvantages. 
     Yes. We don't do this because we want to be able to share our work among others and is easy to backup your work from git onto github. The one disadvantage is that you have to keep the      history of the code between the 2 the same, so it can be a bit of extra work to revert than it normally would.  

  3. What is a repository in Git and how can you create a repository in Git (write out the command(s))? 
  A repository is a storage space for your files that also keeps track of their history and how they change over time.
  -git init
  -git add (filenames)
  -git commit
  

## Coding Exercises 

  You may work on this with your partner or individually. 

  1. Write code to count the total number of `NA` occurrences in the vector `X = c(47,34,33,65,37,NA,43,NA,11,NA,23,NA)`.
  
```{r}
x = c(47,34,33,65,37,NA,43,NA,11,NA,23,NA)
length(which(is.na(x)))
  
```
  

  2. Run the following code: 

```{r}
  age = c(25,30,45,60,12,41)
  smoker = c('T','F','T','F','F','F')
  weight = c(120,137,0,168,91,142)
  example_data = data.frame(age,smoker,weight)
  weight[3] = 150
  weight
```
  This code took three vectors (`age`, `smoker`, and `weight`) and binded them together into an `R` object known as a 
  `data.frame`. The advantage of `data.frame` is that it can handle vectors of different types. For example, age is a numeric 
    vector but smoker status is a character vector (T or F). We named this `data.frame` as `example_data`. I obviously made a
    data entry error: someone cannot have 0 weight. The correct weight should be 150 pounds. Write one line of code that can
    easily correct this using the `[]` syntax. 


  3. In the following I have two code snippets. Turn these code snippets into functions. Think about what each function does
  and what you would name it. How many arguments does it need? 

```{r}
  na_mean = function(vector) {
    return(mean(is.na(x)))
  }
```
  One argument. 
  
```{r}
  percentage_of_sum = function(vector) {
    return(x / sum(x, na.rm = TRUE))
  }
```
  One argument
  
4. Write a function named `both_na()`. This function take two vectors of the same length and returns the number of positions that have an `NA` value in both vectors. 

```{r}
  both_na = function(v1, v2) {
    if (length(v1)==length(v2)){
      return (length(which(is.na(v1[which(is.na(v2))]))))
    }
    else 
      return ("Please give vectors of same length")
  }
```
