---
title: "owner_EthanWanlass.Rmd"
author: "Ethan Wanlass"
date: "9/5/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Name? 
Ethan Wanlass

What do you tell people about your field of study at a party? 
I'm a math major, I don't really tell people about my field of study, people tend not to like talking about it.  

What are the three most important tools/strategies you use for organizing your work? 
  - Keep clear concise paths, folders and filenames. 
  - Space out your work. Easier to read makes work go faster. 
  - Give outlines beforehand so you can figure out the main points you want to address. 

Interesting fact about yourself? 
I'm deaf in my left ear. 

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
